FAIR Theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2024-12-19 manuscript.Rmd
Update manuscript.Rmd
Co-authored-by: Felix Schönbrodt <felix@nicebread.de>

Given these concerns, it is unfortunate that scientific reform initiated by the open science movement has focused primarily on improving deductive methods.
The equally critical inductive processes of theory construction and theory improvement have been largely overlooked.
The present paper restores balance by applying, for the first time,
open science principles to psychological theory.
We apply the FAIR principles to scientific theories,
introducing the concept of *FAIR Theory* to 
facilitate transparent scholarly communication and accelerate cumulative knowledge acquisition.

>>>>

Given these concerns, it is an imbalance that scientific reform initiated by the open science movement has focused primarily on improving deductive methods.
The equally critical inductive processes of theory construction and theory improvement have been largely overlooked.
The present paper restores balance by applying, for the first time,
open science principles to psychological theory.
We apply the FAIR principles to scientific theories,
introducing the concept of *FAIR Theory* to 
facilitate transparent scholarly communication and accelerate cumulative knowledge acquisition.
